Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-05-16 tex/ms.tex
tweaks to new model equation and text

The Right Thing To Do is to express the \emph{reason} that the RPI
believes the spectroscopic data to be less reliable \emph{within} the
likelihood function.
That is, the RPI must add nuisance parameters to parameterize the
unreliability of the spectroscopy, and infer those along with the
parameters of interest.
If this parameterization is good, the information in the spectroscopy
data will not flow entirely to the parameters of interest; instead,
some will flow to the nuisance parameters.
This will reduce the importance of the spectroscopy relative to the
photometry and the RPI will be well pleased with the dominance of the
photometric data in the final inferences of the parameters of
interest.
In this what follows, we provide an example of this kind of
parameterization and inference.

@@

To demonstrate the effectiveness of our spectrophotometric calibration
strategy we will infer the parameters $\theta$ from a spectrum both
\emph{before} and \emph{after} it has been spectrophotometrically
calibrated using typical techniques and ancillary spectrophotometric
calibration data. ( CITE NC)

\subsection{Test Data}
The data we use to test our method consists of MMT Hectospec
spectroscopy of XX stellar clusters in M31 for which YY-band HST
photometric data exist.  The optical spectra were obtained by
\citet{caldwell}.  The wavelength range of the spectra is $3700-7200
\AA$. The instrumental resolution is $\sim 5\AA$ across the optical
range \citep{fabricant13}.  Sky subtraction happened.  We got data
which were uncalibrated and data which had been approximately
spectrophotometrically calibrated using an average for the night (MORE
HERE).

@@

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  +
\sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-(\lambda - \lambda_i)^2/(2\sigma_e^2)}
\\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$.  
The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
where the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods.

@@

We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and the MILES stellar spectral library.  The model
spectra are smoothed by convolution with a Gaussian in wavelength
space (to model the MMT line-spread function) and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift.

@@

@@

Apparently we get really nice redshift/velocity constraints.

>>>>

The Right Thing To Do is to express the \emph{reason} that the RPI
believes the spectroscopic data to be less reliable \emph{within} the
likelihood function.
That is, the RPI must add nuisance parameters to parameterize the
unreliability of the spectroscopy, and infer those along with the
parameters of interest.
If this parameterization is good, the information in the spectroscopy
data will not flow entirely to the parameters of interest; instead,
some will flow to the nuisance parameters.
This will reduce the importance of the spectroscopy relative to the
photometry and the RPI will be well pleased with the dominance of the
photometric data in the final inferences of the parameters of
interest.
In what follows, we provide an example of this kind of
parameterization and inference.

@@

To demonstrate the effectiveness of our spectrophotometric calibration
strategy we will infer the parameters $\theta$ from a spectrum both
\emph{before} and \emph{after} it has been spectrophotometrically
calibrated using typical techniques and ancillary spectrophotometric
calibration data.

\subsection{Test Data}

@@

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
subtraction happened.  We got data which were uncalibrated and data
which had been approximately spectrophotometrically calibrated using
an average for the night (MORE HERE).  Show figure of calibrated and
uncalibrated data.  Discuss S/N, sky subtraction, calibration.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
where the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods.

@@

We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and the MILES stellar spectral library \citep{MILES}.  The model
spectra are smoothed by convolution with a Gaussian in wavelength
space (to model the MMT line-spread function) and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry.

@@

Apparently we get really nice redshift/velocity constraints for free.
